DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-26 paper/main.tex
Update template and abstract

\usepackage{microtype}%if unwanted, comment out or use option "draft"

@@

\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\maketitle
\thispagestyle{empty}
\begin{abstract}
We present DeepPicar, a low-cost deep neural network (DNN) based
autonomous car platform. DeepPicar is a small scale
replication of a real self-driving car called Dave-2 by NVIDIA, which
drove on public roads using a deep convolutional neural network (CNN), 
that takes images from a front-facing camera as input and produces
car steering angles as output. DeepPicar uses the exact same network
architecture---9 layers, 27 million connections and 250K
parameters---and can be trained to drive itself, in real-time, using a
web camera and a modest Raspberry Pi 3 quad-core platform.
Using DeepPicar, we analyze the Pi 3's computing capabilities to 
support end-to-end deep learning based real-time control of autonomous
vehicles. We also systematically compare other contemporary embedded
computing platforms using the DeepPicar's CNN based real-time control
software as a workload. 
We find all tested platforms, including the Pi 3, are capable of
supporting deep-learning based real-time control, from 20 Hz up to 100
Hz depending on hardware platform. 
However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms.
\end{abstract}

>>>>

\usepackage{microtype}%if unwanted, comment out or use option "draft"
\usepackage{adjustbox}

@@

\subjclass{C.4 PERFORMANCE OF SYSTEMS}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Self-driving car, CNN, Raspberry Pi 3}% mandatory: Please provide 1-5 keywords
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\maketitle
\thispagestyle{empty}
\begin{abstract}
We present DeepPicar, a low-cost deep neural network (DNN) based
autonomous car platform. DeepPicar is a small scale
replication of a real self-driving car called Dave-2 by NVIDIA, which
drove on public roads using a deep convolutional neural network (CNN), 
that takes images from a front-facing camera as input and produces
car steering angles as output. DeepPicar uses the exact same network
architecture---8 layers, 27 million connections and 250K
parameters---and can be trained to drive itself, in real-time, using a
web camera and a modest Raspberry Pi 3 quad-core platform.
Using DeepPicar, we analyze the Pi 3's computing capabilities to 
support end-to-end deep learning based real-time control of autonomous
vehicles. We also systematically compare other contemporary embedded
computing platforms using the DeepPicar's CNN based real-time control
software as a workload. 
We find all tested platforms, including the Pi 3, are capable of
supporting deep-learning based real-time control, from 20 Hz up to 100
Hz depending on hardware platform. 
However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms.
\end{abstract}
